---
title: "Neftel-score"
author: "KHJ"
date: '2021 2 17 '
output: html_document
---

## R Markdown
```{r}
require(ggplot2); require(plotly)
require(dplyr); require(tibble)
require(Seurat)

time=score@meta.data$batch %>% strsplit("_") %>% lapply(., `[`, 1) %>% as.character() %>% as.data.frame()
batch=score@meta.data$batch %>% strsplit("_") %>% lapply(., `[`, 2) %>% as.character() %>% as.data.frame()
cellType=score@meta.data$celltype %>% as.data.frame()

SCopc=score@meta.data$NEFTEL_OPC1 %>% as.data.frame()
SCnpc=score@meta.data$NEFTEL_NPC1 %>% as.data.frame()
SCac=score@meta.data$NEFTEL_AC1 %>% as.data.frame()
SCmes=score@meta.data$NEFTEL_MES1 %>% as.data.frame()

tempDf=bind_cols(time, batch, cellType, SCopc, SCnpc, SCac, SCmes) %>% setNames(c("time","rep", "cellType", "SCopc", "SCnpc", "SCac", "SCmes"))

tempDf = tempDf %>% mutate(D=(pmax(SCopc, SCnpc)-pmax(SCac, SCmes)))

#OPC/NPC-enriched
opcNpcDf = tempDf %>% filter(D>0) %>% mutate(X=(sign(SCnpc-SCopc)*log2(abs(SCnpc-SCopc)+1)))
#opcNpcDf = tempDf %>% filter(D>0) %>% mutate(X=(SCnpc-SCopc))

#AC/MES-enriched
acMesDf = tempDf %>% filter(D<0) %>% mutate(X=(sign(SCmes-SCac)*log2(abs(SCmes-SCac)+1)))
#acMesDf = tempDf %>% filter(D<0) %>% mutate(X=(SCmes-SCac))

neftelDf=bind_rows(opcNpcDf, acMesDf)
```
my_cols <- c("pre-CC1"= '#F8766D', "pre-CC2"= '#ad180e', "CC1"='#cf9c63', "CC2"= '#de7b37', "CC3"='#d1c630', 
             "CC4"='#8FAA00', "NSC"=  '#edeb53', "TAC"= '#66d99c', "NB"=  '#00bc59', "Neuron"= '#038741', "OPC"= '#00BADE',  
             "COP"=  '#2194db', "OL"='#2f3bbd',  "EPC"= '#737372', "EC"='#B385FF', "PC"= '#D874FD', "VSMC"='#EF67EB', 
             "MAC"='#f5bfd0', "MG"='#d1889f', "TAM1"= '#ad4565', "TAM2"= '#992c4e', "Meninges"='#360816')
my_cols22 <- my_cols[order(as.integer(names(my_cols)))]

## For Visualization
```{r}
colnames(neftelDf)
tac = subset(neftelDf, cellType == "TAC")
nb = subset(neftelDf, cellType == "NB")
opc = subset(neftelDf, cellType == "OPC")
cop = subset(neftelDf, cellType == "COP")
cop = subset(neftelDf, cellType == "COP")
nsc = subset(neftelDf, cellType == "NSC")
pc = subset(neftelDf, cellType == "PC")

neftelDf %>% ggplot(., aes(x=X, y=D, colour=cellType)) + geom_point(alpha=0.3, size=0.5, color='#c4c4c2')+ geom_point(data=tac, aes(X, D), color=c('#66d99c'), size=0.5) + geom_point(data=nb, aes(X, D), color=c('#00bc59'), size=0.5) + theme_bw() + coord_fixed(xlim=c(-1.5,1.5), ylim=c(-1.5,1.5)) + geom_vline(xintercept = 0, linetype="dotted") +geom_hline(yintercept = 0, linetype="dotted") + labs(x = "Meta-module score", y = "Meta-module score")

neftelDf %>% ggplot(., aes(x=X, y=D, colour=cellType)) + geom_point(alpha=0.3, size=0.5, color='#c4c4c2')+ geom_point(data=opc, aes(X, D), color=c('#00BADE'), size=0.5) + geom_point(data=cop, aes(X, D), color=c('#2194db'), size=0.5) + theme_bw() + coord_fixed(xlim=c(-1.5,1.5), ylim=c(-1.5,1.5)) + geom_vline(xintercept = 0, linetype="dotted") +geom_hline(yintercept = 0, linetype="dotted") + labs(x = "Meta-module score", y = "Meta-module score")

neftelDf %>% ggplot(., aes(x=X, y=D, colour=cellType)) + geom_point(alpha=0.3, size=0.5, color='#c4c4c2')+ geom_point(data=nsc, aes(X, D), color=c('#edeb53'), size=0.5) + theme_bw() + coord_fixed(xlim=c(-1.5,1.5), ylim=c(-1.5,1.5)) + geom_vline(xintercept = 0, linetype="dotted") +geom_hline(yintercept = 0, linetype="dotted") + labs(x = "Meta-module score", y = "Meta-module score")

neftelDf %>% ggplot(., aes(x=X, y=D, colour=cellType)) + geom_point(alpha=0.3, size=0.5, color='#c4c4c2')+ geom_point(data=pc, aes(X, D), color=c('#D874FD'), size=0.5) + theme_bw() + coord_fixed(xlim=c(-1.5,1.5), ylim=c(-1.5,1.5)) + geom_vline(xintercept = 0, linetype="dotted") +geom_hline(yintercept = 0, linetype="dotted") + labs(x = "Meta-module score", y = "Meta-module score")



neftelDf %>% ggplot(., aes(x=X, y=D, colour=cellType)) + geom_point(alpha=0.3, size=0.5, color='#c4c4c2')+ geom_point(data=tac, aes(X, D), color=c('#66d99c'), size=0.5) + geom_point(data=nb, aes(X, D), color=c('#00bc59'), size=0.5) + geom_point(data=opc, aes(X, D), color=c('#00BADE'), size=0.5) + geom_point(data=cop, aes(X, D), color=c('#2194db'), size=0.5) + geom_point(data=nsc, aes(X, D), color=c('#edeb53'), size=0.5) + geom_point(data=pc, aes(X, D), color=c('#D874FD'), size=0.5)  + theme_bw() + coord_fixed(xlim=c(-1.5,1.5), ylim=c(-1.5,1.5)) + geom_vline(xintercept = 0, linetype="dotted") +geom_hline(yintercept = 0, linetype="dotted") + labs(x = "Meta-module score", y = "Meta-module score")


#neftelDf %>% ggplot(., aes(x=X, y=D, colour=cellType)) + geom_point(alpha=0.8, size=1) + theme_bw() + facet_wrap(cellType ~ ., ncol=3) + coord_fixed(xlim=c(-1.5,1.5), ylim=c(-1.5,1.5)) ++
```
```{r}

#my_cols <- c("pre-CC1"= '#F8766D', "pre-CC2"= '#ad180e', "CC1"='#cf9c63', "CC2"= '#de7b37', "CC3"='#d1c630', 
#             "CC4"='#8FAA00', "NSC"=  '#edeb53', "TAC"= '#66d99c', "NB"=  '#00bc59', "Neuron"= '#038741', "OPC"= '#00BADE',  
#             "COP"=  '#2194db', "OL"='#2f3bbd',  "EPC"= '#737372', "EC"='#B385FF', "PC"= '#D874FD', "VSMC"='#EF67EB', 
#             "MAC"='#f5bfd0', "MG"='#d1889f', "TAM1"= '#ad4565', "TAM2"= '#992c4e', "Meninges"='#360816')

precc1 = subset(neftelDf, cellType == "pre-CC1")
precc2 = subset(neftelDf, cellType == "pre-CC2")
cc1 = subset(neftelDf, cellType == "CC1")
cc2 = subset(neftelDf, cellType == "CC2")
cc3 = subset(neftelDf, cellType == "CC3")
cc4 = subset(neftelDf, cellType == "CC4")


neftelDf %>% ggplot(., aes(x=X, y=D, colour=cellType)) + geom_point(alpha=0.3, size=0.5, color='#c4c4c2')+ geom_point(data=cc1, aes(X, D), color=c('#cf9c63'), size=0.5) + geom_point(data=cc2, aes(X, D), color=c('#de7b37'), size=0.5) + theme_bw() + coord_fixed(xlim=c(-1.5,1.5), ylim=c(-1.5,1.5)) + geom_vline(xintercept = 0, linetype="dotted") +geom_hline(yintercept = 0, linetype="dotted") + labs(x = "Meta-module score", y = "Meta-module score")

neftelDf %>% ggplot(., aes(x=X, y=D, colour=cellType)) + geom_point(alpha=0.3, size=0.5, color='#c4c4c2') + geom_point(data=cc3, aes(X, D), color=c('#d1c630'), size=0.5) + geom_point(data=cc4, aes(X, D), color=c('#8FAA00'), size=0.5) + theme_bw() + coord_fixed(xlim=c(-1.5,1.5), ylim=c(-1.5,1.5)) + geom_vline(xintercept = 0, linetype="dotted") +geom_hline(yintercept = 0, linetype="dotted") + labs(x = "Meta-module score", y = "Meta-module score")

neftelDf %>% ggplot(., aes(x=X, y=D, colour=cellType)) + geom_point(alpha=0.3, size=0.5, color='#c4c4c2')+ geom_point(data=precc1, aes(X, D), color=c('#F8766D'), size=0.5) + geom_point(data=precc2, aes(X, D), color=c('#ad180e'), size=0.5) + theme_bw() + coord_fixed(xlim=c(-1.5,1.5), ylim=c(-1.5,1.5)) + geom_vline(xintercept = 0, linetype="dotted") +geom_hline(yintercept = 0, linetype="dotted") + labs(x = "Meta-module score", y = "Meta-module score")



neftelDf %>% ggplot(., aes(x=X, y=D, colour=cellType)) + geom_point(alpha=0.3, size=0.5, color='#c4c4c2')+ geom_point(data=cc1, aes(X, D), color=c('#cf9c63'), size=0.5) + theme_bw() + coord_fixed(xlim=c(-1.5,1.5), ylim=c(-1.5,1.5)) + geom_vline(xintercept = 0, linetype="dotted") +geom_hline(yintercept = 0, linetype="dotted") + labs(x = "Meta-module score", y = "Meta-module score")

neftelDf %>% ggplot(., aes(x=X, y=D, colour=cellType)) + geom_point(alpha=0.3, size=0.5, color='#c4c4c2')+ geom_point(data=cc2, aes(X, D), color=c('#de7b37'), size=0.5) + theme_bw() + coord_fixed(xlim=c(-1.5,1.5), ylim=c(-1.5,1.5)) + geom_vline(xintercept = 0, linetype="dotted") +geom_hline(yintercept = 0, linetype="dotted") + labs(x = "Meta-module score", y = "Meta-module score")

neftelDf %>% ggplot(., aes(x=X, y=D, colour=cellType)) + geom_point(alpha=0.3, size=0.5, color='#c4c4c2')+ geom_point(data=cc3, aes(X, D), color=c('#d1c630'), size=0.5) + theme_bw() + coord_fixed(xlim=c(-1.5,1.5), ylim=c(-1.5,1.5)) + geom_vline(xintercept = 0, linetype="dotted") +geom_hline(yintercept = 0, linetype="dotted") + labs(x = "Meta-module score", y = "Meta-module score")

neftelDf %>% ggplot(., aes(x=X, y=D, colour=cellType)) + geom_point(alpha=0.3, size=0.5, color='#c4c4c2')+ geom_point(data=cc4, aes(X, D), color=c('#8FAA00'), size=0.5) + theme_bw() + coord_fixed(xlim=c(-1.5,1.5), ylim=c(-1.5,1.5)) + geom_vline(xintercept = 0, linetype="dotted") +geom_hline(yintercept = 0, linetype="dotted") + labs(x = "Meta-module score", y = "Meta-module score")


neftelDf %>% ggplot(., aes(x=X, y=D, colour=cellType)) + geom_point(alpha=0.3, size=0.5, color='#c4c4c2')+ geom_point(data=precc1, aes(X, D), color=c('#F8766D'), size=0.5) + theme_bw() + coord_fixed(xlim=c(-1.5,1.5), ylim=c(-1.5,1.5)) + geom_vline(xintercept = 0, linetype="dotted") +geom_hline(yintercept = 0, linetype="dotted") + labs(x = "Meta-module score", y = "Meta-module score")

neftelDf %>% ggplot(., aes(x=X, y=D, colour=cellType)) + geom_point(alpha=0.3, size=0.5, color='#c4c4c2')+ geom_point(data=precc2, aes(X, D), color=c('#ad180e'), size=0.5) + theme_bw() + coord_fixed(xlim=c(-1.5,1.5), ylim=c(-1.5,1.5)) + geom_vline(xintercept = 0, linetype="dotted") +geom_hline(yintercept = 0, linetype="dotted") + labs(x = "Meta-module score", y = "Meta-module score")


```
